---
title: "Week 5: Factors and strings and dates, oh my!"
description: |
  This week, we'll add to our data wrangling toolkit. You'll learn how to efficiently work with and manipulate factors, character strings, and date/times.
date: 10-11-2021
preview: week05.png
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 2
draft: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)
library(magick)
library(magrittr)
```

```{r include=FALSE, cache=TRUE}
hex_paths <- here("img", c("forcats.png", "stringr.png", "lubridate.png"))
read_append <- hex_paths %>%
  magick::image_read() %>%
  magick::image_append()
magick::image_write(read_append, "week05.png")
```

## Monday, 11 Oct

### Topics

Working with factors

### Materials

[Factors slides](https://stat220-fa21.github.io/class_materials/slides/12-factors-forcats.pdf)

[Your turn .Rmd](https://stat220-fa21.github.io/class_materials/activities/12-factors.Rmd)


### Before next time

1. Read [R4DS Chapter 14](https://r4ds.had.co.nz/strings.html) - just get a feel for things, regular expressions are tricky!

1. Work on homework


## Wednesday, 13 Oct

### Topics

Working with strings


### Materials

Slides coming soon


### Before next time

1. Read [R4DS Chapter 16](https://r4ds.had.co.nz/dates-and-times.html#dates-and-times)

1. Finish homework


## Friday, 15 Oct

### Announcements

Homework 5 is due today at 8:30 am

### Topics

Working with dates and times

### Materials

Slides coming soon

### Before next time