---
title: "Week 4: Tidy data"
description: |
 This week we will continue our discussion of data manipulation by focusing on tidying data sets.  what tidy data sets look like and the tools to tidy a data set. We will also talk about reading data into R and working with factors. On Friday, we have our first quiz.
date: 10-04-2021
preview: week04.png
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 2
draft: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)
library(magick)
library(magrittr)
```

```{r include=FALSE, cache=TRUE}
hex_paths <- here("img", c("dplyr.png", "readr.png", "tidyr.png"))
read_append <- hex_paths %>%
  magick::image_read() %>%
  magick::image_append()
magick::image_write(read_append, "week04.png")
```

## Monday, 4 Oct

### Topics

- Joining data sets

- Importing data via `readr`

### Materials

[Data import slides](https://stat220-fa21.github.io/class_materials/slides/09-import.pdf)

[Rmd for data import your turns](https://stat220-fa21.github.io/class_materials/activities/08-import.Rmd)

[Collaborative notes](https://docs.google.com/document/d/1ceP_yo2qLkB80qzOvUuUrfRv4WEZRkv_kMQyOb-BRQI/edit?usp=sharing)

### Before next time

1. Read [R4DS Chapter 12](https://r4ds.had.co.nz/tidy-data.html)

1. Work on homework 4

1. Study for quiz 1



## Wednesday, 6 Oct

### Topics

- Tidy data

- Reshaping data (pivoting, separating)

### Materials

[Tidy data slides](https://stat220-fa21.github.io/class_materials/slides/10-tidy-data.pdf)

[Collaborative notes](https://docs.google.com/document/d/1E2odZeAigFSozdUbmyC_EoLkquE0Fui_WMPALYIEuYg/edit?usp=sharing)

[Rmd for your turns](https://stat220-fa21.github.io/class_materials/activities/09-tidy-data.Rmd)


### Before next time

1. Finish homework 4

1. Finish mini project 1

1. Study for quiz 1



## Friday, 8 Oct

### Announcements

- Homework 4 is due today by noon tomorrow (due to maize issues)

- Mini project 1 is due today by 8:30 am

- I will post Homework 5 today

### Topics

- Joining data sets

- Quiz 1 (last 30 minutes)


### Materials

[Joining example .Rmd file](https://stat220-fa21.github.io/class_materials/activities/08-joins.Rmd)

[Collaborative notes](https://docs.google.com/document/d/1p1-Ejvsldat6-adwGd4_4T3j1jSRgiW2VR4v-e4Eltw/edit?usp=sharing)

[Solution to joining example](https://stat220-fa21.github.io/class_materials/activities/08-soln-joins.pdf)


### Before next time

1. Start homework 5

1. Read [R4DS Chapter 15](https://r4ds.had.co.nz/factors.html)


