---
title: "Week 3: Data viz and data wrangling"
description: |
  This week we'll conclude our initial discussion of static data visualization by
  working through a few special plot types (e.g., maps). We'll also start wrangling
  data sets.
preview: week03.png
date: 09-27-2021
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 2
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)
library(magick)
library(magrittr)
hex_paths <- here("img", c("github.png", "dplyr.png"))
read_append <- hex_paths %>%
  magick::image_read() %>%
  magick::image_append()
magick::image_write(read_append, "week03.png")
```

## Monday, 27 Sept

### Topics

Wrapping up data viz

- Chloropleth maps

- ggplot2 extensions

GitHub collaboration


### Materials

[Mapping slides](https://stat220-fa21.github.io/class_materials/slides/06-maps.pdf)

[Github collabortion slides](https://stat220-fa21.github.io/class_materials/slides/07-git-collaboration.pdf)

[Collaborative notes](https://docs.google.com/document/d/1vIJT1l9ydQww84ieW_ukXm7EAPKVQoN85VB6Pu5m0ug/edit?usp=sharing)

Code to load the `animal.csv` file:

```{r echo=TRUE}
animal <- readr::read_csv("https://stat220-fa21.github.io/class_materials/data/animal.csv")
```



### Before next time

1. Read [sections 5.1-5.5 of R4DS](https://r4ds.had.co.nz/transform.html#transform). 

1. Work on homework 3




## Wednesday, 29 Sept


### Topics

- Introduction to data wrangling via dplyr

- Single table verbs

### Materials

[Slides](https://stat220-fa21.github.io/class_materials/slides/08-wrangle-single-table.pdf)

[Collaborative notes](https://docs.google.com/document/d/1dPFWwaPJuLCWnDB_LeHsWVV4daTQn8MIekoykTGAMto/edit?usp=sharing)

[Rmd for your turns](https://stat220-fa21.github.io/class_materials/activities/07-dplyr.Rmd)

### Before next time

1. Finish homework 3




## Friday, 1 Oct


### Announcements

Homework 3 is due today. Push to Github by the start of class.

### Topics

- More single table verbs

- The pipe operator

- Data import (if time permits)

### Materials

[Slides](https://stat220-fa21.github.io/class_materials/slides/08-wrangle-single-table.pdf) - We will continue from where we left off

[Data import slides](https://stat220-fa21.github.io/class_materials/slides/09-import.pdf)

[Data import your turn](https://stat220-fa21.github.io/class_materials/activities/08-import.Rmd)

### Before next time

1. Start homework 4

1. Work on mini project 1

1. Watch the below videos on joining data (here are the slides) or read [Irizzary chapter 22](https://rafalab.github.io/dsbook/joining-tables.html), whichever works best for your learning style.

<iframe src="https://carleton.hosted.panopto.com/Panopto/Pages/Embed.aspx?id=6ce5348e-71c0-4126-a7e4-ab9c013d71f7&autoplay=false&offerviewer=true&showtitle=true&showbrand=false&captions=false&interactivity=none" height="405" width="720" style="border: 1px solid #464646;" allowfullscreen allow="autoplay"></iframe>
